The Resonance Fourier Transform (RFT):\\ Unitary Lens for Compression, Crypto,\\ and Quantum-Inspired Computing

### 2025-11-25 paper.tex
Add Zenodo DOI: 10.5281/zenodo.17712905
- Added DOI badge to README
- Updated CITATION.cff with DOI and v1.0.0-rft-paper
- Added DOI link to paper author block
- Rebuilt PDF with DOI information

\author{
  Luis M.~Minier\\
  Independent Researcher\\
  Email: \texttt{luisminier79@gmail.com}\\
  GitHub: \url{https://github.com/mandcony/quantoniumos}
}

>>>>

\author{
  Luis M.~Minier\\
  Independent Researcher\\
  Email: \texttt{luisminier79@gmail.com}\\
  GitHub: \url{https://github.com/mandcony/quantoniumos}\\
  DOI: \href{https://doi.org/10.5281/zenodo.17712905}{10.5281/zenodo.17712905}
}
